Parity-odd Neutrino Torque Detection

### 2018-10-24 neu_torque.tex
5sigma

Measured from simulations, $(\alpha_1,\alpha_2,\alpha_3)=(-0.18,0.18,0.02)$ in Eq.(\ref{eq.Ir}) optimizes the cross-correlation $\left\langle\spin^I_{\nu 0}\cdot\spin^{I_r}_\nu\right\rangle=0.19$. In this case we need $4\times 10^8$ halos to have a $1\sigma$ detection (see Appendix A). If we improve the reconstruction of $\I_R$, the lower limit of required halos is $1.7\times 10^7$.

>>>>

Measured from simulations, $(\alpha_1,\alpha_2,\alpha_3)=(-0.18,0.18,0.02)$ in Eq.(\ref{eq.Ir}) optimizes the cross-correlation $\left\langle\spin^I_{\nu 0}\cdot\spin^{I_r}_\nu\right\rangle=0.19$. In this case we need $5\times 10^9$ halos to have a $5\sigma$ detection (see Appendix A). If we improve the reconstruction of $\I_R$, the lower limit of required halos is $2\times 10^8$.
